Forecasting the 2024 US Presidential Election

### 2024-11-04 paper/paper.qmd
Updated introduction and appendix formatting

In our models, we identified eight pivotal swing states—Georgia, Michigan, Nevada, New Hampshire, North Carolina, Pennsylvania, and Wisconsin—crucial for predicting the 2024 election outcome. We constructed Bayesian generalized linear models to estimate the percentage likelihood of candidates Trump and Harris winning in these states, incorporating education level, gender distribution, ethnic demographics, historical voting patterns, approval ratings of Joe Biden, and current leanings toward Trump or Harris. Our election forecast resulted in 6 out of 8 pivotal states, as well as the national polling average, leaning towards the Republican party.

@@

## Measurement  
We chose Emerson as our primary pollster, and the reasoning for this is detailed in @sec-appendix. Emerson's polls offered crucial information, such as polling dates, party affiliations, sample sizes, and the percentage of support for each political party.

@@

# Appendix {#sec-appendix}

## Appendix A: Pollster Methodology Overview {-}
Emerson College Polling was initially a college polling exercise and is now an "innovative, nationally-ranked" non-partisan polling center (@AboutUs). For the 2024 USA Presidential Election pollster, the Emerson College Polling defined the population to be "likely voters" of 2024 United States Presidential Election. Emerson College Polling does indicate that the targeted population of "likely voters" is based on "2024 Likely Voter Modeling." However, the methodology for this modelling and the specific model is not indicated, so we can't determine the scope of the targeted population (@Polling).

@@

## Appendix B: Idealized Survey Design for $100K Budget {-}

>>>>

In our models, we identified eight pivotal swing states—Georgia, Michigan, Nevada, New Hampshire, North Carolina, Pennsylvania, and Wisconsin—crucial for predicting the 2024 election outcome. We constructed Bayesian generalized linear models to estimate the percentage likelihood of candidates Trump and Harris winning in these states, incorporating education level, gender distribution, ethnic demographics, historical voting patterns, and current leanings toward Trump or Harris. Our election forecast resulted in 6 out of 8 pivotal states, as well as the national polling average, leaning towards the Republican party.

@@

## Measurement  
We chose Emerson as our primary pollster, and the reasoning for this is detailed in @sec-appendix-A. Emerson's polls offered crucial information, such as polling dates, party affiliations, sample sizes, and the percentage of support for each political party.

@@

# Appendix {#sec-appendix-A}

## Pollster Methodology Overview {-}
Emerson College Polling was initially a college polling exercise and is now an "innovative, nationally-ranked" non-partisan polling center (@AboutUs). For the 2024 USA Presidential Election pollster, the Emerson College Polling defined the population to be "likely voters" of 2024 United States Presidential Election. Emerson College Polling does indicate that the targeted population of "likely voters" is based on "2024 Likely Voter Modeling." However, the methodology for this modelling and the specific model is not indicated, so we can't determine the scope of the targeted population (@Polling).

@@

# Appendix: Idealized Survey Design for $100K Budget {#sec-appendix-B}
